---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "60%",
  warning = FALSE
)
```

# eriespatial

<!-- badges: start -->
![R badge](https://img.shields.io/badge/R-276DC3?style=for-the-badge&logo=r&logoColor=white)
![develoment badge](https://img.shields.io/badge/Dev-InProgress-<COLOR>.svg)
<!-- badges: end -->

The goal of eriespatial is to provide common Lake Erie shapefiles for R users. Shapefiles have generally been imported as an `sf` object and also plotted as a base `ggplot2` object. The `sf` objects follow the naming convention of `shape_[area]`. The `ggplot2` objects follow the naming convention of `base_[area]`.

## Installation

You can install the development version of eriespatial from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LakeErie-PreyFish-Acoustics/eriespatial")
```

## Example
```{r example}
library(eriespatial)
library(sf)
library(ggplot2)
## view the sf shapefile
data("shape_ebstrata")
shape_ebstrata
# plot(shape_ebstrata)
## view ggplot basemap
data("base_ebstrata")
base_ebstrata
```

### Add custom points to base ggplot
```{r addpoints}
pointdata <- data.frame(LON = c(-79.8, -80, -79.2), LAT = c(42.3, 42.4, 42.7))
pointdata <- st_as_sf(pointdata, coords = c("LON", "LAT"), crs=4269)
base_ebstrata + geom_sf(data = pointdata, color = 'red')
```

